skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-07-19 paper/paper.Rmd
fix @ahhgust name

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2,3"
  - name: August Woener
    affiliation: "2,3"
  - name: Bruce Budowle
    affiliation: "2,3"

>>>>

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2,3"
  - name: August E. Woerner
    affiliation: "2,3"
  - name: Bruce Budowle
    affiliation: "2,3"
